\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
update softmax code; add appendix

	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &19&19  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

	List: Google Image source links

	Table: abnormities with description (edit the two tables below; ALPHABETICAL ORDER!!!)

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{lp{3.8in}}
				\caption{OCT Abnormities}
				\label{tb:oct-abnormites}\\
				\toprule
				Abnormity&Description\\
				\toprule

				\multicolumn{1}{l}{Central serous chorioretinopathy (CSC)}
				& \multicolumn{1}{l}{The accumulation of fluid underneath the retina.}\\

				\multicolumn{1}{l}{Epiretinal membrane (ERM)}
				& A thin layer of fibrous tissue forms on the surface of the retina, particularly the macula.\\

				\multicolumn{1}{l}{Macular hole (MH)}
				& Disruption or discontinuity in the normal retinal layers surrounding the macular hole.\\

				\multicolumn{1}{l}{Stargardt disease}
				& Thinning and atrophy of the retina. Disruption of photoreceptor layers. Presence of subretinal deposits.\\

				\multicolumn{1}{l}{Retinitis pigmentosa (RP)}
				& Thinning of the Retinal Layers. Disruption of Photoreceptor Layers. Attenuation of Retinal Vasculature.\\

				\multicolumn{1}{l}{Macular telangiectasia (Mactel)}
				& Abnormalities in the macular blood vessels, leading to changes in the macular structure and function\\

				\multicolumn{1}{l}{Diabetic macular edema (DME)}
				& The accumulation of fluid in the macula. \\

				\multicolumn{1}{l}{Choroidal neovascularization}
				& The abnormal growth of new blood vessels in the choroid layer.\\

				\multicolumn{1}{l}{Subretinal fluid}
				& The accumulation of fluid between the neurosensory retina and the retinal pigment epithelium (RPE)\\

				\multicolumn{1}{l}{Intraretinal fluid}
				& The accumulation of fluid within the layers of the retina.\\

				\multicolumn{1}{l}{Drusen}
				& Small deposits of extracellular material that accumulate beneath the retinal pigment epithelium (RPE) or between the RPE and the photoreceptor layer in the macular region of the retina.\\

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{lp{3.8in}}
				\caption{Fundus Abnormalities}
				\label{tb:fundus-ab}\\
				\toprule
				Abnormity&Description\\
				\toprule

				\multicolumn{1}{l}{Retinitis pigmentosa (RP)}
				& Description of RP\\

				\multicolumn{1}{l}{Microaneurysm}
				& Description of microaneurysm\\

				\multicolumn{1}{l}{Macular hole (MH)} & Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\

				\multicolumn{1}{l}{Hard exudate} & Yellow or Yellow-White Deposits. Hard Borders. Distribution. Clustering Around Blood Vessels\\

				\multicolumn{1}{l}{Hemorrhage} & Small dot-like to larger blot. Fresh hemorrhages typically appear bright red or deep red in color, indicating the presence of oxygenated blood. Over time, as the blood undergoes degradation and clotting, the hemorrhage may change color to darker red, orange, or yellowish hues.\\

				\multicolumn{1}{l}{Cotton wool patch / soft exudate} & White or off-white lesions. Irregular shapes and margins.\\

				\multicolumn{1}{l}{Vascular abnormity} & Retinal Vessel Tortuosity. Retinal Vessel Caliber Changes. \\

				\multicolumn{1}{l}{Drusen} & Small, round or oval-shaped yellow or white deposits.\\

@@

	TEXT: APP/website description

	Link: GitHub repo

>>>>

	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

	\subsection*{Code}

	The link for the GitHub repository is \url{https://github.com/SiqiPan2008/MAAM/}.

	\subsection*{Results Page}

	\subsection*{Abnormities and Diseases}

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{llp{9.5cm}}
				\caption{OCT Abnormities}
				\label{tb:oct-abnormites}\\
				\toprule
				Abnormity&Abbr.&Description\\
				\toprule

				Choroidal neovascularization
				& CNV
				& The abnormal growth of new blood vessels in the choroid layer.\\

				Central serous chorioretinopathy
				& CSC
				& The accumulation of fluid underneath the retina.\\

				Diabetic macular edema
				& DME
				& The accumulation of fluid in the macula associated with diabetic retinopathy. \\

				Drusen
				& Drusen
				& Small deposits of extracellular material that accumulate beneath the retinal pigment epithelium (RPE) or between the RPE and the photoreceptor layer in the macular region of the retina.\\

				Epiretinal membrane
				& ERM
				& A thin layer of fibrous tissue forms on the surface of the retina, particularly the macula.\\

				Intraretinal fluid
				& IF
				& The accumulation of fluid within the layers of the retina.\\

				Macular hole
				& MH
				& Disruption or discontinuity in the normal retinal layers surrounding the macular hole.\\

				Macular telangiectasia
				& Mactel
				& Abnormities in the macular blood vessels, leading to changes in the macular structure and function.\\

				Retinitis pigmentosa
				& RP
				& Thinning of the retinal layers. Disruption of photoreceptor layers. Attenuation of retinal vasculature.\\

				Stargardt disease
				& ST
				& Thinning and atrophy of the retina. Disruption of photoreceptor layers. Presence of subretinal deposits.\\

				Subretinal fluid
				& SF
				& The accumulation of fluid between the neurosensory retina and the retinal pigment epithelium (RPE)\\

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{llp{11.2cm}}
				\caption{Fundus Abnormalities}
				\label{tb:fundus-ab}\\
				\toprule
				Abnormity&Abbr.&Description\\
				\toprule

				Cotton wool patch
				& CWP
				& White or off-white lesions. Irregular shapes and margins. Also called soft exudates. \\

				Drusen
				& Drusen
				& Small, round or oval-shaped yellow or white deposits.\\

				Hard exudate
				& HE
				& Yellow or Yellow-White Deposits. Hard Borders. Distribution. Clustering Around Blood Vessels\\

				Hemorrhage
				& HM
				& Small dot-like to larger blot. Fresh hemorrhages typically appear bright red or deep red in color, indicating the presence of oxygenated blood. Over time, as the blood undergoes degradation and clotting, the hemorrhage may change color to darker red, orange, or yellowish hues.\\

				Macular hole
				& MH
				& Full-thickness macular hole showing a surrounding cuff of subretinal fluid.\\

				Microaneurysm
				& MA
				& Small vascular dilatations observed in retinal blood vessels, visible as tiny red dots scattered in the retina posteriorly.\\

				Retinitis pigmentosa
				& RP
				& Arteriolar attenuation. Retinal pigmentary changes (either hypopigmentation and/or hyperpigmentation in the form of bone-spicule and pigment clumpings). Waxy disc pallor.\\

				Vascular abnormity
				& VA
				& Retinal Vessel Tortuosity. Retinal Vessel Caliber Changes. \\

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{cc}
				\caption{Diseases}
				\label{tb:diseases}\\
				\toprule
				Disease&Abbr.\\
				\toprule

				Branch or hemi-central retinal vein occlusion&BRVO\\
				Central retinal vein occlusion&CRVO\\
				Central serous chorioretinopathy&CSC\\
				Dry age-related macular degeneration&dAMD\\
				Epiretinal membrane&ERM\\
				Macular telangiectasia&Mactel\\
				Macular hole&MH\\
				Mild diabetic retinopathy&mDR\\
				Referable diabetic retinopathy&rDR\\
				Retinitis pigmentosa&RP\\
				Stargardt disease&ST\\
				Wet age-related macular degeneration&wAMD\\
				\bottomrule
			\end{longtable}
		}
	}

	\subsection*{Image Sources}

	\subsubsection*{OCT -- ERM}
	\vspace{0.5cm}

	\fontsize{6}{0}\selectfont{
	\begin{enumerate}
		\item \url{https://qers.com.au/eye-conditions/epiretinal-membrane-erm/}

		\item \url{https://www.asrs.org/patients/retinal-diseases/19/epiretinal-membranes}

		\item \url{https://theretinagroup.com/epiretinal-membrane/}

		\item \url{https://www.istanbulretina.com/en-diseases-epiretinal-membrane.php}

		\item \url{https://www.mdfoundation.com.au/about-macular-disease/other-macular-conditions/epiretinal-membrane-macular-pucker/}

		\item \url{https://www.researchgate.net/figure/Grading-of-epiretinal-membrane-ERM-by-spectral-domain-optical-coherence-tomography_fig1_351426760}

		\item \url{https://www.singhealth.com.sg/patient-care/conditions-treatments/epiretinal-membrane}

		\item \url{https://www.windycityretina.com/epiretinal-membrane/}

		\item \url{https://retinacentertx.com/conditions/macular-pucker}

		\item \url{https://www.rvscny.com/patient-eduction/conditions-we-treat/epiretinal-membrane/}

		\item \url{https://www.lyneye.co.za/epiretinal-membrane-erm/}

		\item \url{https://rehmansiddiqui.com/epi-retinal-membrane-erm/}

		\item \url{https://www.reviewofophthalmology.com/article/when-and-how-to-peel-an-epiretinal-membrane}

		\item \url{https://www.janigianretina.com/retina-conditions/epiretinal-membrane}

		\item \url{https://www.researchgate.net/figure/6-months-later-ERM-with-partial-attachment-to-the-retina_fig2_309566437}

		\item \url{https://www.capefearretina.com/epiretinal-membrane/}
	\end{enumerate}
	}

	\subsubsection*{Fundus -- MH}
	\vspace{0.5cm}

	\fontsize{6}{0}\selectfont{
	\begin{enumerate}
			\item \url{https://emedicine.medscape.com/article/1224320-overview}

			\item \url{https://www.chatswoodeye.com/macular-hole-specialists/}

			\item \url{https://swretina.com/macular-hole/}

			\item \url{https://www.ophthalmologyexpertservices.com/blog/2019/macular-hole}

			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}

			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}

			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}

			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}

			\item \url{https://www.researchgate.net/figure/Fundus-image-of-the-right-eye-of-case-1-a-shows-a-macular-hole-with-associated-retinal_fig1_324657341}

			\item \url{https://www.girayersoz.com.tr/en/macular-hole/}

			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}

			\item \url{https://www.gotzaridis.gr/en/conhttps://www.willseye.org/macular-hole/ditions/macula/full-thickness-macular-hole}

			\item \url{https://www.willseye.org/macular-hole/}

			\item \url{http://www.oculist.net/downaton502/prof/ebook/duanes/pages/v3/ch031/013f.html}

			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#11}

			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#12}

			\item \url{https://www.jaypeedigital.com/book/9788180616532/chapter/ch7}

			\item \url{https://emedicine.medscape.com/article/1224320-clinical?form=fpf}

			\item \url{https://www.jaafarelannanmd.com/macular-hole}

			\item \url{https://asiaeyecentre.com.sg/eye-conditions/the-ageing-eye/macular-hole/}

			\item \url{https://retinaandeye.com.au/eye-conditions/full-thickness-macular-holes/}

			\item \url{https://retinahi.com/interesting-cases/}

			\item \url{https://imagebank.asrs.org/file/2858/traumatic-macular-hole}

			\item \url{https://www.semanticscholar.org/paper/Giant-macular-hole-as-an-atypical-consequence-of-a-Blaise-Comhaire/5c9a60375d904323eb5fbcd52b6bd03b735f6951}

			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/Macular-hole-commotio-retinae-choroidal-rupture.htm#gsc.tab=0}

			\item \url{https://areaoftalmologica.com/en/terms-of-ophthalmology/macular-hole/}

			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}

			\item \url{https://montanaretinaconsultants.com/portfolio/macular-holes/}

			\item \url{https://ccteyes.com/2019/09/30/what-is-a-macular-hole-and-how-does-it-affect-your-vision/}

			\item \url{https://www.backoftheeyemd.com/retina-services/macular-holes/}

			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/extrafoveal-macular-hole/emh-1.jpg}
	\end{enumerate}
	}

	\subsubsection*{Fundus -- RP}
	\vspace{0.5cm}

	\fontsize{6}{0}\selectfont{
		\begin{enumerate}
			\item \url{https://imagebank.asrs.org/file/93471/retinitis-pigmentosa}

			\item \url{https://educate.choroida.com/2021/07/05/retinitis-pigmentosa/}

			\item \url{https://decisionmakerplus.net/dg-post/h35-52-retinitis-pigmentosa/}

			\item \url{https://basicmedicalkey.com/retinitis-pigmentosa/}

			\item \url{https://www.news-medical.net/health/What-is-Retinitis-Pigmentosa.aspx}

			\item \url{https://www.researchgate.net/figure/Fundus-photograph-of-an-individual-affected-with-retinitis-pigmentosa-The-fundus_fig3_40447070}

			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F15/}

			\item \url{https://www.brainkart.com/article/Retinal-Dystrophies--Retinitis-Pigmentosa_26087/}

			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}

			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}

			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}

			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}

			\item \url{https://www.linkedin.com/posts/stevenlevymd_blindness-from-retinitis-pigmentosa-reversed-activity-7047214648877608960-ar4h}

			\item \url{https://atlas-1-elastic.atlasoph.com/photo.jsf;jsessionid=94EF0B6B067E676E8BCB3F2AD7B9885A?node=6475&locale=en}

			\item \url{https://dizziness-and-balance.com/disorders/visual/retinopathy/RP.html}

			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}

			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}

			\item \url{https://eyeandear.org/2020/07/a-new-era-in-retinal-research/}

			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F14/}

			\item \url{https://commons.wikimedia.org/wiki/File:Fundus_of_patient_with_retinitis_pigmentosa,_end_stage.jpg}

			\item \url{https://healthjade.net/retinitis-pigmentosa/}

			\item \url{https://www.reviewofoptometry.com/article/night-spots}

			\item \url{https://www.visualsurgery.com/eye-conditions/retinal-diseases/other-retinal-diseases/retinitis-pigmentosa/}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://emedicine.medscape.com/article/1227488-overview?form=basic}

			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

			\item \url{https://webvision.med.utah.edu/book/electrophysiology/the-electroretinogram-clinical-applications/}

			\item \url{https://www.retinarevealed.com/retinitis-pigmentosa-page-34-of-49/}

			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}

			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}

			\item \url{https://www.nyp.org/advances/article/ophthalmology/retinitis-pigmentosa-mitigating-retinal-degeneration-with-crispr-technology}

			\item \url{https://www.ehu.eus/en/-/pacientes-con-retinosis-pigmentaria-en-la-pole}

			\item \url{https://en.wikipedia.org/wiki/Retinal_degeneration_%28rhodopsin_mutation%29}

			\item \url{https://imagebank.asrs.org/file/29807/x-linked-retinitis-pigmentosa}

			\item \url{https://educate.choroida.com/2023/04/07/choroideremia-unveiling-what-you-need-to-know/}

			\item \url{https://retinography.org/retinitis-pigmentosa-2/}

			\item \url{https://retinography.org/retinitis-pigmentosa-2/}

			\item \url{https://retinography.org/retinitis-pigmentosa/}

			\item \url{https://retinography.org/retinitis-pigmentosa/}
		\end{enumerate}
	}
